A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-03-01 for_submission/rvaught_2018.tex
02/28/2018

The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the trough of the line blueward. To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement a two velocity component ``flow" model in tandem with a single ``fixed-velocity", with respect to the central wavelength of \ion{Mg}{2}, model to quantify the absorption line kinematics. The qualitative conetext of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}. Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

\subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
\textbf{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. IN addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} detected significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.   Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material}

>>>>

The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the valley of the line blueward. To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement a two velocity component ``flow" model in tandem with a single ``fixed-velocity", with respect to the central wavelength of \ion{Mg}{2}, model to quantify the absorption line kinematics. The qualitative conetext of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}. Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

\subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
\textbf{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. In addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} showed significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies. Photoionization modeling of the observed strength of emission suggests that a secondary source of \ion{Mg}{2} emission is nebular emission from HII regions. Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material}
